\documentclass{tufte-book}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\title{Fizika  \thanks{Zahvaljujući vama.}}
\author[Google]{Mr. Fizičar}
\publisher{Učenicima srednjih škola}

\usepackage{lipsum}
\usepackage{isotope}
\usepackage{booktabs}
\usepackage{titlesec}
\usepackage{graphicx}
\setkeys{Gin}{width=\linewidth,totalheight=\textheight,keepaspectratio}
\graphicspath{{multimedija/}}
\usepackage{mandi}
\usepackage{units}
\usepackage{amsmath,amsfonts,amsthm} % Math packages
\usepackage{mathtools}% http://ctan.org/pkg/mathtools
%\usepackage{mparhack}
\usepackage{sectsty} % Allows customizing section commands
\usepackage[dvipsnames]{xcolor}
\usepackage{pgf,tikz}
\usepackage{pgfplots}
\usetikzlibrary{shapes,arrows}
\usetikzlibrary{patterns,fadings}
\usetikzlibrary{arrows}
\usetikzlibrary{decorations.pathreplacing}
\usetikzlibrary{decorations.markings}
\usetikzlibrary{snakes}
\usetikzlibrary{spy}
\usepackage{setspace}
\usepackage{3dplot}
\usepackage{cancel}
\usepackage{physymb}
\usepackage{braket}
\usepackage{verbatim}
\usepackage{fancyvrb}
\fvset{fontsize=\normalsize}

\newcommand{\hangp}[1]{\makebox[0pt][r]{(}#1\makebox[0pt][l]{)}}

\newcommand{\hangstar}{\makebox[0pt][l]{*}}

\usepackage{xspace}
\usepackage{makeidx}
\makeindex

\newcommand{\vdqi}{\textit{VDQI}\xspace}
\newcommand{\ei}{\textit{EI}\xspace}
\newcommand{\ve}{\textit{VE}\xspace}
\newcommand{\be}{\textit{BE}\xspace}
\newcommand{\VDQI}{\textit{The Visual Display of Quantitative Information}\xspace}
\newcommand{\EI}{\textit{Envisioning Information}\xspace}
\newcommand{\VE}{\textit{Visual Explanations}\xspace}
\newcommand{\BE}{\textit{Beautiful Evidence}\xspace}

\newcommand{\TL}{Tufte-\LaTeX\xspace}


%\newcommand{\monthyear}{%
	%\ifcase\month\or January\or February\or March\or April\or May\or June\or
	%July\or August\or September\or October\or November\or
	%December\fi\space\number\year
%}
\usepackage{datetime}

\newdateformat{monthdayyeardate}{%
	\THEDAY. \THEMONTH. \THEYEAR. }

\newcommand{\openepigraph}[2]{%
	%\sffamily\fontsize{14}{16}\selectfont
	\begin{fullwidth}
		\sffamily\large
		\begin{doublespace}
			\noindent\allcaps{#1}\\% epigraph
			\noindent\allcaps{#2}% author
		\end{doublespace}
	\end{fullwidth}
}

\newcommand{\blankpage}{\newpage\hbox{}\thispagestyle{empty}\newpage}

\usepackage{units}

\renewcommand{\contentsname}{Sadržaj}
\renewcommand{\figurename}{Slika}
\renewcommand{\chaptername}{}
\newcommand{\measure}[3]{#1/#2$\times$\unit[#3]{pc}}

\newcommand{\hlred}[1]{\textcolor{Maroon}{#1}}% prints in red
\newcommand{\hangleft}[1]{\makebox[0pt][r]{#1}}
\newcommand{\hairsp}{\hspace{1pt}}% hair space
\newcommand{\hquad}{\hskip0.5em\relax}% half quad space
\newcommand{\TODO}{\textcolor{red}{\bf TODO!}\xspace}
\newcommand{\ie}{\textit{i.\hairsp{}e.}\xspace}
\newcommand{\eg}{\textit{e.\hairsp{}g.}\xspace}
\newcommand{\na}{\quad--}% used in tables for N/A cells
\providecommand{\XeLaTeX}{X\lower.5ex\hbox{\kern-0.15em\reflectbox{E}}\kern-0.1em\LaTeX}
\newcommand{\tXeLaTeX}{\XeLaTeX\index{XeLaTeX@\protect\XeLaTeX}}

% \index{\texttt{\textbackslash xyz}@\hangleft{\texttt{\textbackslash}}\texttt{xyz}}
\newcommand{\tuftebs}{\symbol{'134}}% a backslash in tt type in OT1/T1
\newcommand{\doccmdnoindex}[2][]{\texttt{\tuftebs#2}}% command name -- adds backslash automatically (and doesn't add cmd to the index)
\newcommand{\doccmddef}[2][]{%
	\hlred{\texttt{\tuftebs#2}}\label{cmd:#2}%
	\ifthenelse{\isempty{#1}}%
	{% add the command to the index
		\index{#2 command@\protect\hangleft{\texttt{\tuftebs}}\texttt{#2}}% command name
	}%
	{% add the command and package to the index
		\index{#2 command@\protect\hangleft{\texttt{\tuftebs}}\texttt{#2} (\texttt{#1} package)}% command name
		\index{#1 package@\texttt{#1} package}\index{packages!#1@\texttt{#1}}% package name
	}%
}% command name -- adds backslash automatically
\newcommand{\doccmd}[2][]{%
	\texttt{\tuftebs#2}%
	\ifthenelse{\isempty{#1}}%
	{% add the command to the index
		\index{#2 command@\protect\hangleft{\texttt{\tuftebs}}\texttt{#2}}% command name
	}%
	{% add the command and package to the index
		\index{#2 command@\protect\hangleft{\texttt{\tuftebs}}\texttt{#2} (\texttt{#1} package)}% command name
		\index{#1 package@\texttt{#1} package}\index{packages!#1@\texttt{#1}}% package name
	}%
}% command name -- adds backslash automatically
\newcommand{\docopt}[1]{\ensuremath{\langle}\textrm{\textit{#1}}\ensuremath{\rangle}}% optional command argument
\newcommand{\docarg}[1]{\textrm{\textit{#1}}}% (required) command argument
\newenvironment{docspec}{\begin{quotation}\ttfamily\parskip0pt\parindent0pt\ignorespaces}{\end{quotation}}% command specification environment
\newcommand{\docenv}[1]{\texttt{#1}\index{#1 environment@\texttt{#1} environment}\index{environments!#1@\texttt{#1}}}% environment name
\newcommand{\docenvdef}[1]{\hlred{\texttt{#1}}\label{env:#1}\index{#1 environment@\texttt{#1} environment}\index{environments!#1@\texttt{#1}}}% environment name
\newcommand{\docpkg}[1]{\texttt{#1}\index{#1 package@\texttt{#1} package}\index{packages!#1@\texttt{#1}}}% package name
\newcommand{\doccls}[1]{\texttt{#1}}% document class name
\newcommand{\docclsopt}[1]{\texttt{#1}\index{#1 class option@\texttt{#1} class option}\index{class options!#1@\texttt{#1}}}% document class option name
\newcommand{\docclsoptdef}[1]{\hlred{\texttt{#1}}\label{clsopt:#1}\index{#1 class option@\texttt{#1} class option}\index{class options!#1@\texttt{#1}}}% document class option name defined
\newcommand{\docmsg}[2]{\bigskip\begin{fullwidth}\noindent\ttfamily#1\end{fullwidth}\medskip\par\noindent#2}
\newcommand{\docfilehook}[2]{\texttt{#1}\index{file hooks!#2}\index{#1@\texttt{#1}}}
\newcommand{\doccounter}[1]{\texttt{#1}\index{#1 counter@\texttt{#1} counter}}



\begin{document}
	
	% Front matter
	\frontmatter
	
	% r.1 blank page
	%\blankpage
	
	% v.2 epigraphs
	\newpage\thispagestyle{empty}
	\openepigraph{%
		I think that modern physics has definitely decided in favor of Plato. In fact the smallest units of matter are not physical objects in the ordinary sense; they are forms, ideas which can be expressed unambiguously only in mathematical language.
	}{Werner Heisenberg%, {\itshape Design, Form, and Chaos}
	}
	\vfill
	\openepigraph{%
		The only shibboleth the West has is science. It is the premise of modernity and it defines itself as a rationality capable of, indeed requiring separation from politics, religion and really, society. Modernisation is to work towards this\ldots If one looks at the works of Newton to Einstein, they were never scientists in the way modernity understands the term. 
	}{Bruno Latour}
	\vfill
	\openepigraph{%
		The boundary between science fiction and social reality is an optical illusion.
	}{Donna Haraway}
	
	
	% r.3 full title page
	\maketitle
	
	
	% v.4 copyright page
	\newpage
	\begin{fullwidth}
		~\vfill
		\thispagestyle{empty}
		\setlength{\parindent}{0pt}
		\setlength{\parskip}{\baselineskip}
		Copyright \copyright\ \the\year\ \thanklessauthor
		
		\par\smallcaps{Objavljeno \thanklesspublisher}
		
		\par\smallcaps{https://github.com/rumi55/Fizika}
		
		\par Licensed under the Apache License, Version 2.0 (the ``License''); you may not
		use this file except in compliance with the License. You may obtain a copy
		of the License at \url{http://www.apache.org/licenses/LICENSE-2.0}. Unless
		required by applicable law or agreed to in writing, software distributed
		under the License is distributed on an \smallcaps{``AS IS'' BASIS, WITHOUT
			WARRANTIES OR CONDITIONS OF ANY KIND}, either express or implied. See the
		License for the specific language governing permissions and limitations
		under the License.\index{license}
		
		\par\textit{Zadnja izmjena, \monthdayyeardate\today}
	\end{fullwidth}

	% r.5 contents
	\tableofcontents

	

	
	
	% r.9 introduction
	\cleardoublepage
	\chapter*{Napomena}
	
	Ova FIZIKA je projekat započet od strane učitelja fizike iz BiH koji su željni promjena.  Knjiga je pisana u \LaTeX \-u koristeći se otvorenim kodom \doccls{tufte-book} i \doccls{tufte-handout} za pisanje.  
	
	\vspace{2cm}
	
	https://github.com/rumi55/Fizika
	
	%%
	% Start the main matter (normal chapters)
	\begin{fullwidth}
		\include{uvod/predgovor}
	\end{fullwidth}

	\mainmatter

	\include{uvod/vektori}
	\include{elektrostatika/uvod}
	\include{elektrostatika/elektrostaticke-pojave}
	%\include{elektrostatika/elektroskop}
	\include{elektrostatika/zakon-o-ocuvanju-naboja}
	\include{elektrostatika/kulonov-zakon}
	\include{elektrostatika/elektricno-polje}
	\include{elektrostatika/jacina-elektricnog-polja}
	\include{elektrostatika/linije-sile-elektricnog-polja}
	\include{elektrostatika/elektricno-polje-zemlje}
	\include{elektrostatika/elektricni-fluks}
	\include{elektrostatika/rad-u-elektricnom-polju}
	\include{elektrostatika/elektricni-potencijal}
	\include{elektrostatika/elektricni-napon}
	\include{elektrostatika/ekvipotencionalna-povrsina}
	\include{elektrostatika/kretanje-naboja-u-elektricnom-polju}
	\include{elektrostatika/elektricna-infuluencija}
	\include{elektrostatika/elektricni-kapacitet}
	\include{elektrostatika/elektricni-kondenzatori}
	\include{elektrostatika/vezivanje-kondenzatora}
	\include{elektrostatika/energija-elektricnog-polja}
	\include{elektrostatika/dielektrici-u-elektricnom-polju}
	\include{elektrostatika/elektricna-struja}
	
\printindex
\end{document}